---
title: "Object Oriented Programming"
output: html_notebook
---

# Programming Paradigms

Programming paradigms differ in what's the fundamental focus of your thoughts. In functional programming, you focus on the functions that will do a different set of tasks that will lead you to a goal. In OOP, your focus is on an initial piece of data, what you must store, and the methods (i.e., functions used on the object) that you´ll need to efficiently handle the object in question. 

OOP is preferrable when you have a limited number of complex objects. e.g., Bioconductor. 

## OOP: what you've already seen.

Object oriented programming is great for building tools for data analysis, not for the data analysis itself. For example, you may have to summarize different objects, and want a different behavior for each one. You accomplish such with OOP. Think of the difference in calling summary on a data-frame and a linear model. 

## OOP: Systems to use.

S3 and R6 are the most common and useful OOP systems in R. S3 such that functions work differntly according to the object; R6 for more tricks. 


```{r}
(matrix <- matrix(c(1, 2, 3, 4)),)
```

```{r}
class(matrix)
```

```{r}
typeof(matrix)
```

### Overriding the class

```{r}
(random <- runif(n = 10, min = 0, max = 1))
```

```{r}
class(random)
```

```{r}
class(random) <- "Random_Numbers"
class(random)
```

```{r}
random
```

However, you won't break basic functionality. 

```{r}
mean(random)
```

